The mass of the substructure in the ``Jackpot'' Gravitational Lens

### 2016-11-07 doc/Paper2/ms.tex
Moved stuff around
newer mnras template

\documentclass[useAMS,usenatbib]{mn2e}

\voffset=-0.8in

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
%\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{color}

\usepackage{epstopdf}

% For revisions
\newcommand{\revisions}{}
\newcommand{\revisionstwo}{}

\title[]
{The mass of the substructure in the ``Jackpot'' Gravitational Lens}

\author[Brewer, Huijser and Lewis]{%
  Brendon~J.~Brewer$^{1}$\thanks{To whom correspondence should be addressed. Email: {\tt bj.brewer@auckland.ac.nz}},
  David Huijser$^{1}$,
  Geraint F. Lewis$^2$
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand\\
  $^2$Sydney Institute for Astronomy, School of Physics, A28,
  The University of Sydney, NSW 2006, Australia}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\date{}

\maketitle

\label{firstpage}

\begin{abstract}

\end{abstract}

\begin{keywords}
gravitational lensing: strong --- methods: data analysis --- methods: statistical
\end{keywords}

\section{Introduction}

@@

\begin{thebibliography}{99}
\end{thebibliography}

\end{document}

>>>>

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

\usepackage{microtype}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[]
{The mass of the substructure in the ``Jackpot'' Gravitational Lens}

\author[Brewer, Huijser and Lewis]{%
  Brendon~J.~Brewer$^{1}$\thanks{To whom correspondence should be addressed. Email: {\tt bj.brewer@auckland.ac.nz}},
  David Huijser$^{1}$,
  Geraint F. Lewis$^2$
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand\\
  $^2$Sydney Institute for Astronomy, School of Physics, A28,
  The University of Sydney, NSW 2006, Australia}
% These dates will be filled out by the publisher
\date{}

% Enter the current year, for the copyright statements etc.
\pubyear{2016}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
gravitational lensing: strong --- methods: data analysis --- methods: statistical
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}
Obscuration of a light source by foreground material is a common
phenomenon in astronomy, and appears on scales ranging from
{\bf blah blah blah...}

When the obscuring material is in motion as observed from Earth,
the observed brightness of an unresolved source will fluctuate with time
as different parts of the source are blocked.

In this paper we describe

\section{Hypothesis Space}
Our modelling assumptions are intended as a compromize between flexibility
(so we can potentially infer the presence of complex structures)
and computational tractability.

Consider a coordinate system $(x,y)$ in units of the star's radius.
The surface brightness profile
$S(x, y)$ of the star uses the limb darkening profile
\begin{align}
S(x, y) &\propto
    \left\{
        \begin{array}{lr}
            1 - b\left(1 - \sqrt{1 - (x^2 + y^2)}\right),   & x^2+y^2 \leq 1\\
            0, & \textnormal{otherwise}
        \end{array}
    \right.
\end{align}
where $b$ is a limb darkening parameter.

The density profile of the obscuring material is composed of a sum of
$N$ circular ``blobs'' based on the blob profile
used by \citet{lensing2}. A single blob of width $w$ and total ``mass'' $M$
(the integral of the density profile),
positioned at the origin, would have density profile
\begin{align}
\rho(x, y) &= \left\{
        \begin{array}{lr}
            \frac{2M}{\pi w^2}\left(1 - \frac{r^2}{w^2}\right), & r \leq w\\
            0, & \textnormal{otherwise}
        \end{array}\right.
\end{align}
where $r = \sqrt{x^2 + y^2}$. The total density profile of $N$ blobs,
with masses $\{M_i\}$ and centers $\{(x_i, y_i)\}$, is
\begin{align}
\rho(x, y) &= \sum_{i=1}^N
        \left\{
        \begin{array}{lr}
            \frac{2M_i}{\pi w_i^2}
                \left(1 - \frac{r_i^2}{w_i^2}\right), & r_i \leq w_i\\
            0, & \textnormal{otherwise}
        \end{array}\right.
\end{align}
where $r_i = \sqrt{(x - x_i)^2 + (y - y_i)^2}$ is the distance of a point
in the $x-y$ plane from the central position $(x_i, y_i)$ of blob $i$.

If the blob density is taken as the optical depth, then the overall image
of the star is
\begin{align}
I(x, y) &= S(x, y)e^{-\rho(x,y)}
\end{align}
and the observed total flux of the star is
\begin{align}
F &= \int_{-\infty}^{\infty}\int_{-\infty}^{\infty}
        I(x, y) \, dx \, dy\\
  &= \int_{-\infty}^{\infty}\int_{-\infty}^{\infty}
        S(x, y)e^{-\rho(x,y)} \, dx \, dy.
\end{align}
We define the normalizing constant of the star's surface brightness profile
such that the total flux of the star would be 1 in the absence of any
obscuration.

\subsection{Motion of the obscurers}
As the obscuring blobs are in motion, we need to be able to calculate the
flux of the star {\em as a function of time}. If the obscurers
are initially centered around $(x_0, 0)$ and move to the right
at speed $v$, the observed flux of the star at time $t > 0$ will be
\begin{align}
F(t) &= \int_{-\infty}^{\infty}\int_{-\infty}^{\infty}
          S(x, y)e^{-\rho\left(x - (x_0 + vt), y\right)} \, dx \, dy.
\end{align}
which we recognize as the convolution of $S$ with $e^{-\rho}$, evaluated
at $(x_0 + vt, 0)$:
\begin{align}
F(t) &= \left.\left(S * e^{-\rho}\right)\right|_{(x_0 + vt, 0)}.
\end{align}
This formulation is computationally convenient. Instead of having to
simulate the motion of the blobs, we can instead convolve the image of
the star with the image of the blobs, and evaluate the result at a series
of points corresponding to the timestamps in the data.
The convolution can be done using Fast Fourier Transforms.

\section{Prior information}
In this section we list the assumed prior information, that is,
the joint prior distribution for the unknown hyperparameters
$\boldsymbol{\alpha}$, parameters $\boldsymbol{\theta}$,
and data $\boldsymbol{D}$. The joint prior distribution is usually factorized
as follows:
\begin{align}
p(\boldsymbol{\alpha}, \boldsymbol{\theta}, \boldsymbol{D})
    &= p(\boldsymbol{\alpha})p(\boldsymbol{\theta}|\boldsymbol{\alpha})
        p(\boldsymbol{D} | \boldsymbol{\theta}, \boldsymbol{\alpha})\\
    &= p(\boldsymbol{\alpha})p(\boldsymbol{\theta}|\boldsymbol{\alpha})
        p(\boldsymbol{D} | \boldsymbol{\theta}).
\end{align}

\subsection{The limb darkening parameter}

\section{Demonstration on `easy' simulated data}

\section{Demonstration on `hard' simulated data}

\section{Application to KIC*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{references} % if your bibtex file is called example.bib

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

%\appendix
%\section{Some extra material}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex
